Investigate poor coverage for ash.hu

### 2015-11-05 analysis/investigate_hu_badcoverage.Rmd
fixed loading of example

```{r}
  eg=load_example(dsc_shrink,42,"flat-top",method="ash.hu.s","../output")
  eg$output$fitted.g
```

@@

Can we find an example?
```{r}
  table((ash.u.s.spiky %>% filter(value==0))$seed)
  eg =load_example(dsc_shrink,seed = 39,method="ash.u.s",scenario="spiky","../output")
```

>>>>

```{r}
  eg=load_example(dsc_shrink,42,"flat-top",method="ash.hu.s","../output/dsc-shrink-files/")
  eg$output$fitted.g
```

@@

Can we find an example?
```{r}
  table((ash.u.s.spiky %>% filter(value==0))$seed)
  eg =load_example(dsc_shrink,seed = 39,method="ash.u.s",scenario="spiky","../output/dsc-shrink-files")
```
